### 2021-06-04 paper/report.tex
Add figures to be combined. Fix some label issues.

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small Model description}}
        \label{fig:change_working_hours_by_edu}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/disease_progression.png}
        \caption{Disease progression}
        \label{fig:disease_progression}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        Stringency index + multipliers

@@

@@

        Fraction of pupils with antigen tests

        Fraction of workers with antigen tests

        Fraction of vaccinations (effective = lagged by two weeks or date of vaccination?)

@@

        % \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small Tests and vaccinations}}
        \label{fig:pcr_antigen_tests_vaccinations}
    \end{subfigure}
    \vskip3ex

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        % \includegraphics[width=\textwidth]{../figures/disease_progression.png}
        Share known cases (estimated)

        Share B.1.1.7

@@

        % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small TBD}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}
    \vskip3ex

>>>>

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small Model description}}
        \label{fig:model_graph}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/disease_progression.png}
        \caption{Disease progression}
        \label{fig:disease_progression}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/work_multiplier_since_sep}

        Stringency index + multipliers

@@

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/share_of_educ_participants_with_rapid_test}

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/share_of_workers_with_rapid_test_offer_at_work}
        % fraction of workers must be multiplied with 0.6 because only that many actually
        % accept the offer

        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_individuals_with_first_vaccine}

        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_receiving_vaccination_per_day}

@@

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:pcr_antigen_tests_vaccinations}
    \end{subfigure}
    \vskip3ex

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_b117_acc_to_rki}

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/assumed_overall_share_known_cases}

@@

        % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small TBD}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex
